---
title: "Cronchbach's alpha and FAs on scales"
output:
  pdf_document:
    toc: yes
    toc_depth: 2
    keep_tex: yes
  header-includes:
  - \usepackage{dcolumn}
  - \usepackage{array}
  keep_md: yes
---

```{r load packages, warning = FALSE, message = FALSE, echo=FALSE}
  knitr::opts_chunk$set(warning = FALSE, message = FALSE)
suppressPackageStartupMessages(library(lavaan))
suppressPackageStartupMessages(library(tidyverse))
suppressPackageStartupMessages(library(readxl))
suppressPackageStartupMessages(library(tsibble))
suppressPackageStartupMessages(library(dplyr))
suppressPackageStartupMessages(library(DT))
suppressPackageStartupMessages(library(knitr))
suppressPackageStartupMessages(library(psych)) # psychometrics

```



```{r, echo=FALSE}
knitr::opts_chunk$set(warning = FALSE, message = FALSE)
moduletwo <- read_excel(here::here("thesis_surveydata/political_factors_complete.xlsx"))
save(moduletwo, file = "moduletwo.rda")
module2 <- data.frame(moduletwo)
module2[module2 == "Rather not say/ Don't know"] <- "Rather not say/Don't know"
#module2 %>% filter(!row_number() %in% c(1,2))

# loaded data set for module 2 eco -pol variables and removes the rows with question number and question text
```


```{r, eval =TRUE, echo=FALSE}
knitr::opts_chunk$set(warning = FALSE, message = FALSE)
#This chunk contains the coding schemes of various scales used in survey one: eco-political factors, kahan scale and acceptance scale
codedmodule2 <- module2 %>%
  
#remove row 1
  filter(!row_number() %in% c(1,2)) %>% 
  
# replace risky likert scale with numbers
  mutate_at(vars(starts_with("Risky")), funs(case_when(. =="Not at all risky" ~ 1, 
                                                       . =="Slightly risky" ~ 2, 
                                                       . =="Moderately risky" ~ 3, 
                                                       . =="Very risky" ~ 4, 
                                                       . =="Extremely risky" ~ 5))) %>%

# replace beneficial likert scale with numbers  
  mutate_at(vars(starts_with("Ben")), funs(case_when(. =="Not at all beneficial" ~ 1,
                                                     . =="Slightly beneficial" ~ 2,
                                                     . =="Moderately beneficial" ~ 3,
                                                     . =="Very beneficial" ~ 4,
                                                     . =="Extremely beneficial" ~ 5 ))) %>%

# replace nuclear acceptance likert scale with numbers
  mutate_at(vars(N_accept,N_reluctantlyaccept,N_reject), funs(case_when(. == "Strongly disagree" ~ 1, 
                                                                        . == "Somewhat disagree" ~ 2,
                                                                        . == "Neither agree nor disagree" ~3,
                                                                        . == "Somewhat agree" ~ 4,
                                                                        . == "Strongly agree" ~ 5))) %>%
  
# code likert scale for variables for Kahan scale into numbers
  mutate_at(vars(starts_with (c("K_I","K_H","DISPLACE", "POLLUTE", "HEALTH", "JOBS", "BEAUTY", "PRIDE", "NPRIDE", "DEV", "PROSPER", "RELY"))), funs(case_when(. == "Strongly disagree" ~ 1, 
               . == "Somewhat disagree" ~ 2,
               . == "Neither agree nor disagree" ~3,
               . == "Somewhat agree" ~ 4,
               . == "Strongly agree" ~ 5))) %>%
  
# reverse code for likert scale for variables for Kahan scale into numbers
mutate_at(vars(starts_with (c("K_S","K_E"))), funs(case_when(. == "Strongly disagree" ~ 5, 
                                                               . == "Somewhat disagree" ~ 4,
                                                               . == "Neither agree nor disagree" ~3,
                                                               . == "Somewhat agree" ~ 2,
                                                               . == "Strongly agree" ~ 1))) %>%

# code eco-pol scale variables into numbers
  mutate_at(vars(SYSTEMDEMO,SYSTEMRELIGION,SYSTEMTECHNO,SYSTEMTOTAL,WEALTHLIM,MECHANISATION,DECISIONDECEN,INDUSTRYSMALL,ECONOMYLOCAL,ENVOVERDEV,OWNERPUB, OWNERREG), funs(case_when(. == "Strongly disagree" ~ 1, 
                        . == "Somewhat disagree" ~ 2,
                        . == "Neither agree nor disagree" ~3,
                        . == "Somewhat agree" ~ 4,
                        . == "Strongly agree" ~ 5))) %>%

# reverse code eco-pol scale variables into numbers 
 mutate_at(vars(DECISIONCEN,INDUSTRYLARGE,ECONOMYGLOBAL,OWNERPVT,OWNERNOREG), funs(case_when(. == "Strongly disagree" ~ 5, 
                                                                                                         . == "Somewhat disagree" ~ 4,
                                                                                                         . == "Neither agree nor disagree" ~3,
                                                                                                         . == "Somewhat agree" ~ 2,
                                                                                                         . == "Strongly agree" ~ 1)))
```
\newpage

# Kahan et al (2007) scale

## Cronbach's alpha test on the Kahan et al (2007) scale

**Kahan et al (2007) scale**

Individualism - Communitarinism 

- **K_IINTRFER**	The government interferes far too much in our everyday lives.
- **K_IPRIVACY**	The government should stop telling people how to live their lives.
- **K_IPROTECT**	It’s not the government’s business to try to protect people from themselves.
- **K_SHARM**	    Sometimes the government needs to make laws that keep people from hurting themselves.
- **K_SLIMCHOI**	The government should put limits on the choices individuals can make so they don’t get in the way of what’s good for society.
- **K_SPROTECT**	The government should do more to advance society’s goals, even if that means limiting the freedom and choices of individuals.

Hierarchy -Egalitarianism

- **K_HEQUAL**	  We have gone too far in pushing equal rights in this country.
- **K_HREVDIS1**	Nowadays it seems like there is just as much discrimination against upper castes as there is against Dalits.
- **K_EDISCRIM**	Discrimination against minorities is still a very serious problem in our society.
- **K_ERADEQ1**	  We need to dramatically reduce inequalities between the rich and the poor.
- **K_EWEALTH**	  Our society would be better off if the distribution of wealth was more equal.
- **K_ERADEQ2**	  We need to dramatically reduce inequalities between men and women.


KahanI weak alpha = 0.29, KahanS strong alpha = 0.71
Hierarchy -Egalitarianism strong alpha = 0.71
reasons for this could be that the individualism items are not well adapted to the Indian population 
final items alpha =  0.75

```{r, echo=FALSE}
knitr::opts_chunk$set(warning = FALSE, message = FALSE)

library(ltm)

#cronbach's alpha for the entire Kahan scale


Kahan <- codedmodule2 %>%
  dplyr::select(starts_with(c("K_S", "K_I", "K_H", "K_E")))%>%
  na.omit()

Kahan.alpha <- psych::alpha(Kahan, check.keys = TRUE)

#summary(Kahan.alpha)

#cronbach's alpha for Individualism - Communitarinism scale

KahanSI <- codedmodule2 %>%
  dplyr::select(starts_with(c("K_S", "K_I")))%>%
  na.omit()

KahanSI.alpha <- psych::alpha(KahanSI, check.keys = TRUE) #Alpha = 0.49

#summary(KahanSI.alpha)

KahanS <- codedmodule2 %>%
  dplyr::select(starts_with(c("K_S")))%>%
  na.omit()


KahanI <- codedmodule2 %>%
  dplyr::select(starts_with(c("K_I")))%>%
  na.omit()


KahanI.alpha <- psych::alpha(KahanI, check.keys = TRUE)

KahanS.alpha <- psych::alpha(KahanS, check.keys = TRUE)

# KahanI weak alpha = 0.29, KahanS strong alpha = 0.71
# reasons for this could be that the individualism items are not well adapted to the Indian population 


KahanHE <- codedmodule2 %>%
  dplyr::select(starts_with(c("K_H", "K_E")))%>%
  na.omit()


KahanHE.alpha <- psych::alpha(KahanHE, check.keys = TRUE)

#summary(KahanHE.alpha)

Kahanfas <- codedmodule2 %>%
  dplyr::select(K_SLIMCHOI, K_SPROTECT, K_SHARM, K_HEQUAL, K_ERADEQ1, K_EWEALTH, K_ERADEQ2)%>%
  na.omit()

Kahanfas.alpha <- psych::alpha(Kahanfas, check.keys = TRUE)

#summary(Kahanfas.alpha)
#Alpha 0.75

# Hierarchy -Egalitarianism strong alpha = 0.71

```

\newpage

# CFA on the Kahan scale 

Since this a well used scale with theoretical basis for factor distinctions and there are also previous studies that used the same scale I did CFA not exploratory FA. 
```{r, echo=FALSE}

# CFA for Kahan scale. We shouldn't do FA here since this a well used scale with theoretical basis for factor distinctions and there are also previous studies that used the same scale 

Kahan <- codedmodule2 %>%
  dplyr::select(starts_with(c("K_")))%>%
  na.omit()

Kahan_fas <- '
  KahanS =~ K_SHARM + K_SLIMCHOI + K_SPROTECT 
  KahanH =~ K_ERADEQ1 + K_EWEALTH + K_ERADEQ2
'

# Run CFA with standardization all method - gives standardized loadings 
# The factors are assumed to be correlated 

Kahan_cfa <- cfa(Kahan_fas, data = Kahan, std.lv = TRUE)

# Print the summary of the CFA results, including fit measures
summary(Kahan_cfa, fit.measure= TRUE, standardized = TRUE)

# RMSEA - between 0.05 and 0.08 (reasonable fit), less than 0.05 close fit and greater than 0.10 is poor fit 
# CFI - greater than 0.90 or 0.95 indicates good fit
#TFI - CFI>TFI >0.90 - indicates good fit


# after having removed a few variables that had very low loading, the model is now a good fit, we have two latent variables - Hierarchy- egalitarian and Communitarian. Again we see that individualistic variables just don't fit here. 

# creating table of factor scores 

Kahan_scores <- predict(Kahan_cfa, newdata = Kahan)

Kahan_Kscores <- cbind(Kahan, Kahan_scores)





```
\newpage

# Eco-pol value scale

**Scale 1 : The economic -political values of the perceiver**

- **DECISIONDECEN**	 Local politicians shouldn't have to ask permission from the central government to implement policies
- **DECISIONCEN**	   Laws and policies would be implemented more smoothly if more power lay with the central government.
- **SYSTEMTOTAL**	   It is good to have a strong leader who does not have to bother with elections.
- **SYSTEMTECHNO**	 Experts, not the government, should make decisions according to what they think is best for the country.
- **SYSTEMDEMO**	   It is very important to have a democratic political system because it ensures that no individual leader has too much power.
- **SYSTEMRELIGION** There should be a system governed by religious law.
- **INDUSTRYSMALL**	 Large corporations are destroying the local industries in India and benefiting only a handful of people.
- **INDUSTRYLARGE**	 Large scale industries are required for the development of the country that will benefit everyone
- **ECONOMYLOCAL**	 India would be better off if foreign companies didn't come to here
- **ECONOMYGLOBAL**	 Foreign companies have led to a range of benefits for the Indian people and society
- **DEVOVERENV**	   Economic growth and creating jobs should be prioritized over environmental protection
- **ENVOVERDEV**	   Polluting industries that spoil the environment should be shut down even if it costs people their jobs
- **OWNERPVT**	     All businesses and industries should be owned privately
- **OWNERPUB**	     The government should own most large businesses and industries
- **OWNERREG**	     Regardless of ownership, the government should pass strong regulations and implement them
- **OWNERNOREG**	   There is too much red-tape and the government should not interfere with businesses and industries
- **WEALTHLIM**	     A limit should be put to how much wealth a person can amass
- **MECHANISATION**	 Rapid mechanization of work is taking away jobs from workers in this country


## Cronbach's Alpha Test on Scale 1: Economic -Political Values of the Perceiver


```{r, echo= FALSE}
knitr::opts_chunk$set(warning = FALSE, message = FALSE)
ecopolscalescores <- codedmodule2 %>%
 dplyr::select(starts_with(c("SYSTEMDEMO","SYSTEMRELIGION","SYSTEMTECHNO","SYSTEMTOTAL","WEALTHLIM","MECHANISATION","DECISIONDECEN","DECISIONCEN","INDUSTRYLARGE","INDUSTRYSMALL","ECONOMYGLOBAL","ECONOMYLOCAL", "ENVOVERDEV","DEVOVERENV","OWNERPVT","OWNERNOREG","OWNERPUB", "OWNERREG")))%>%
  na.omit()#%>%
  #dplyr::mutate(Pro_decentralisation = mean(c_across("DECISIONDECEN":"DECISIONCEN")))%>%
   #dplyr::mutate(Pro_largescale = mean(c_across("INDUSTRYLARGE":"INDUSTRYSMALL")))%>%
   #dplyr::mutate(Pro_global = mean(c_across("ECONOMYGLOBAL":"ECONOMYLOCAL")))%>%
   #dplyr::mutate(Pro_ecogrowth = mean(c_across("ENVOVERDEV":"DEVOVERENV")))%>%
   #dplyr::mutate(Pro_private = mean(c_across("OWNERPVT":"OWNERREG")))%>%
  #dplyr::select(!c("DECISIONDECEN","DECISIONCEN", "INDUSTRYLARGE","INDUSTRYSMALL","ECONOMYGLOBAL", "ECONOMYLOCAL","ENVOVERDEV",     "DEVOVERENV","OWNERPVT","OWNERNOREG","OWNERPUB", "OWNERREG"))

#cronbach alpha

ecopol_alpha <- psych::alpha(ecopolscalescores, check.keys = TRUE)

summary(ecopol_alpha)

# Alpha for eco-pol values scale is good at 0.76- the scale has good inner consistency. 

```

\newpage



**Scale 2 : Economic and Political characteristics of the energy technology scale -  Nuclear energy**

- **DISPLACENUCLER** Nuclear energy is leading to displacement of people from their land
- **POLLUTENUCLEAR** Nuclear energy increases pollution of air/water/land
- **HEALTHNUCLEAR**	 Nuclear energy poses a great risk to the health of people living around it
- **JOBSNUCLEAR**	   Nuclear energy will bring jobs to the local community
- **BEAUTYNUCLEAR**	 Nuclear energy spoils the natural beauty of the landscape
- **PRIDENUCLEAR**	 I would be proud if my community used nuclear energy
- **NPRIDENUCLEAR**	 Nuclear energy is a mark of pride for our nation
- **DEVNUCLEAR**	   Nuclear energy pushes forward the country's development
- **PROSPERNUCLEAR** Nuclear energy brings economic prosperity to the surrounding regions
- **RELYNUCLEAR**	   I don't like the idea that I have to rely on the government for electricity from nuclear energy

## Cronbach's alpha test on Scale 2 : Eco-Pol Characteristics of the Technology -  Nuclear Energy

```{r, echo=FALSE}
knitr::opts_chunk$set(warning = FALSE, message = FALSE)

#alpha test on Eco-pol characteristics of the technology

Nuclear <- codedmodule2 %>%
dplyr::select("DISPLACENUCLEAR":"RELYNUCLEAR") %>%
dplyr::rename("Nuclear energy is leading to displacement of people from their land" = "DISPLACENUCLEAR") %>%
dplyr::rename("Nuclear energy increases pollution of air/water/land" = "POLLUTENUCLEAR")%>%
dplyr::rename("Nuclear energy poses a great risk to the health of people living around it" = "HEALTHNUCLEAR")%>%
dplyr::rename("Nuclear energy will bring jobs to the local community" = "JOBSNUCLEAR")%>%
dplyr::rename("Nuclear energy spoils the natural beauty of the landscape" = "BEAUTYNUCLEAR")%>%
dplyr::rename("I would be proud if my community used solar nuclear" = "PRIDENUCLEAR")%>%
dplyr::rename("Nuclear energy is a mark of pride for our nation" = "NPRIDENUCLEAR") %>%
dplyr::rename("Nuclear energy pushes forward the country's development" = "DEVNUCLEAR")%>%
dplyr::rename("Nuclear energy brings economic prosperity to the surrounding regions" = "PROSPERNUCLEAR")%>%
dplyr::rename("I don't like the idea that I have to rely on the government for electricity from (large scale nuclear energy)" = "RELYNUCLEAR")%>%
  na.omit()


nuclear_alpha <- psych::alpha(Nuclear, check.keys = TRUE)

summary(nuclear_alpha)

# std.alpha 0.68 - not very good 




```


## Cronbach's Alpha Test on the Combined Scale. 

```{r, echo = FALSE}

# we combined both the scales, since we are interested in eco-pol factors at large - values of the perceiver and the values perceived in an energy technology.Here I have removed the variables on systems of government.  

ecopolall <- codedmodule2 %>%
        dplyr::select("WEALTHLIM","MECHANISATION","DECISIONDECEN","DECISIONCEN","INDUSTRYLARGE","INDUSTRYSMALL","ECONOMYGLOBAL","ECONOMYLOCAL", "ENVOVERDEV","DEVOVERENV","OWNERPVT","OWNERNOREG","OWNERPUB", "OWNERREG","DISPLACENUCLEAR",  "POLLUTENUCLEAR", "HEALTHNUCLEAR", "JOBSNUCLEAR", "BEAUTYNUCLEAR", "PRIDENUCLEAR", "NPRIDENUCLEAR", "DEVNUCLEAR", "PROSPERNUCLEAR", "RELYNUCLEAR", "SYSTEMDEMO")%>%
  na.omit()#%>%
  #dplyr::mutate(Pro_decentralisation = mean(c_across("DECISIONDECEN":"DECISIONCEN")))%>%
   #dplyr::mutate(Pro_largescale = mean(c_across("INDUSTRYLARGE":"INDUSTRYSMALL")))%>%
  #dplyr::select(!c("DECISIONDECEN","DECISIONCEN", "INDUSTRYLARGE","INDUSTRYSMALL","ECONOMYGLOBAL", "ECONOMYLOCAL","ENVOVERDEV",     "DEVOVERENV","OWNERPVT","OWNERNOREG","OWNERPUB", "OWNERREG"))

ecopolall_alpha <- psych::alpha(ecopolall, check.keys = TRUE)

summary(ecopolall_alpha)

# when we combine both the scales the alpha is high at 0.785 (almost 0.8)

```



\newpage 

# FA on All Ecopol Variables (except systems of governance) 

## Two factor solution : MR1 people centered development and MR2 nationalist development

**MR1 People Centered Development: Pdevelop**

HEALTHNUCLEAR	-  Nuclear energy poses a great risk to the health of people living around it.

BEAUTYNUCLEAR	-  Nuclear energy spoils the natural beauty of the landscape.

MECHANISATION	-  Rapid mechanization of work is taking away jobs from workers in this country.

INDUSTRYSMALL	-  Large corporations are destroying the local industries in India and benefiting only a handful of people.

DISPLACENUCLEAR- Nuclear energy is leading to displacement of people from their land.

POLLUTENUCLEAR-  Nuclear energy increases pollution of air/water/land. 

OWNERREG-        Regardless of ownership, the government should pass strong regulations and implement them.


**MR2 Nationalist Development: Ndevelop**

DEVNUCLEAR	-  Nuclear energy pushes forward the country's development.

PRIDENUCLEAR-  I would be proud if my community used nuclear energy.

NPRIDENUCLEAR- Nuclear energy is a mark of pride for our nation.

PROSPERNUCLEAR-Nuclear energy brings economic prosperity to the surrounding regions.

INDUSTRYLARGE- Large scale industries are required for the development of the country that will benefit everyone.
 
```{r, echo = FALSE}
# FA on all ecopol variables except systems of governance 

#ecopolall_cor <- cor(ecopolall)
#PCA24 <- principal(ecopolall, nfactors = 24, rotate = "none") # no rotation to start with. 

#print(PCA24)

#PCA24$loadings

#fa.parallel(ecopolall_cor)


#PCA2 <- principal(ecopolall, nfactors = 2, rotate = "none") # no rotation to start with. 

#print(PCA2)

#PCA2$loadings


# this suggests 2 factors if we go by FA or 8 by PCA. let's try both and see how they look conceptually 

ecopolall2.fa <- fa(ecopolall, nfactors = 2, rotate = "varimax")

print.psych(ecopolall2.fa, cut = 0.50, sort = TRUE)

#fa.diagram(ecopolall2.fa)

#cor(ecopolall)

# So I am going to extract factor scores and bind them to the dataset

ecopolall_scores <- psych::factor.scores(ecopolall, ecopolall2.fa)

# The factor scores will be stored in the scores element of the returned list
scores1 <- ecopolall_scores$scores


```

\newpage

# FA on Scale 1 - only eco-pol values of the perceiver scale. 

Four Factor Solution -


**MR1 Problems of industrialisation**

MECHANISATION-   Rapid mechanization of work is taking away jobs from workers in this country

OWNERREG-        Regardless of ownership, the government should pass strong regulations and implement them.

WEALTHLIM-	     A limit should be put to how much wealth a person can amass


**MR3 Local Economy And Decision Making**

INDUSTRYSMALL-  Large corporations are destroying the local industries in India and benefiting only a handful of people

ECONOMYLOCAL-   India would be better off if foreign companies didn’t come to here

DECISIONDECEN-  Local politicians shouldn’t have to ask permission from the central government to implement policies


**MR4 Centralised and Large Industry**

DECISIONCEN-   Laws and policies would be implemented more smoothly if more power lay with the central government

ECONOMYGLOBAL- Foreign companies have led to a range of benefits for the Indian people and society

OWNERNOREG- 	 There is too much red-tape and the government should not interfere with businesses and industries

INDUSTRYLARGE- Large scale industries are required for the development of the country that will benefit everyone

**MR2 Development and Business Ownership**

DEVOVERENV-	   Economic growth and creating jobs should be prioritized over environmental protection

OWNERPVT-	     All businesses and industries should be owned privately

OWNERPUB-	     The government should own most large businesses and industries

ENVOVERDEV-	   Polluting industries that spoil the environment should be shut down even if it costs people their jobs


```{r, echo = FALSE}

# below are only eco-pol values of the perceiver scale. 

ecopolval <- codedmodule2 %>%
        dplyr::select("WEALTHLIM","MECHANISATION","INDUSTRYSMALL","ECONOMYGLOBAL", "ENVOVERDEV","OWNERNOREG","OWNERPUB", "OWNERREG", "DECISIONDECEN","DECISIONCEN","INDUSTRYLARGE","ECONOMYLOCAL", "DEVOVERENV","OWNERPVT")%>%
  na.omit()

alpha(ecopolval, check.keys = TRUE) # 0.71

#ncol(ecopolval)  number of cols is 14 

#ecopolval_cor <- cor(ecopolval)
#PCA14 <- principal(ecopolval, nfactors = 14, rotate = "none") # no rotation to start with. 

#print(PCA14)

#PCA14$loadings

#fa.parallel(ecopolval_cor)


# based on the PCA and scree plot we have two options : 
# 1 - we do a factor analysis for 3 factors as suggested by the scree plot 
# 2 - we do factor analysis for 8 components with eigen values for 8 being above 1

#1 
ecopolval4.fa <- fa(ecopolval, nfactors = 4, rotate = "varimax")

print.psych(ecopolval4.fa, cut = 0.40, sort = TRUE)

fa.diagram(ecopolval4.fa)

#cor(ecopolval)

# questions for Terre , 2) 4 factors/3 factors/2 factors - variation explained how should i deal with that. 
# four factor analysis - MR1 - problems of industrialisation MR2 - local economy and decision making MR3 - centralised and large industry MR4- dev/ownership
```

\newpage

# Factor analysis on Scale 2 -  Eco-Pol characteristics of the technology -  Nuclear Energy

Two Factor Solution - positive versus negative characteristics 

**MR1 Negative Characteristics**

HEALTHNUCLEAR	-  Nuclear energy poses a great risk to the health of people living around it.

BEAUTYNUCLEAR	-  Nuclear energy spoils the natural beauty of the landscape.

DISPLACENUCLEAR- Nuclear energy is leading to displacement of people from their land.

POLLUTENUCLEAR-  Nuclear energy increases pollution of air/water/land. 

**MR2 Positive Characteristics**

DEVNUCLEAR-     Nuclear energy pushes forward the country's development.

PRIDENUCLEAR-   I would be proud if my community used nuclear energy.

NPRIDENUCLEAR-  Nuclear energy is a mark of pride for our nation.

PROSPERNUCLEAR- Nuclear energy brings economic prosperity to the surrounding regions.

JOBSNUCLEAR-    Nuclear energy will bring jobs to the local community.

RELYNUCLEAR-    I don't like the idea that I have to rely on the government for electricity from nuclear energy.

```{r, echo=FALSE}
knitr::opts_chunk$set(warning = FALSE, message = FALSE)

#alpha test on Eco-pol characteristics of the technology

Nuclear <- codedmodule2 %>%
dplyr::select("DISPLACENUCLEAR":"RELYNUCLEAR") %>%
  na.omit()

nuclear_alpha <- psych::alpha(Nuclear, check.keys = TRUE)

summary(nuclear_alpha)

# std.alpha 0.68 - not very good 


#ncol(Nuclear)

#Nuclear_cor <- cor(Nuclear)
#PCA10 <- principal(Nuclear, nfactors = 10, rotate = "none") # no rotation to start with. 

#print(PCA10)

#fa.parallel(Nuclear_cor)

Nuclear.fa <- fa(Nuclear, nfactors = 2, rotate = "varimax")

print.psych(Nuclear.fa, cut = 0.40, sort = TRUE)

fa.diagram(Nuclear.fa)


# two options 2 factors or three factors. 2 factors translate to -  positive versus negative characteristics 

# So I am going to extract factor scores an add them bind them to the dataset

Nuclear_scores <- psych::factor.scores(Nuclear, Nuclear.fa)

# The factor scores will be stored in the scores element of the returned list
scores2 <- Nuclear_scores$scores

#binding factor scores to the dataset

Nuclear_with_scores <- cbind(Nuclear, scores2)



```
\newpage

# Solar - FA 2 factor solution 


here I'll make the same chart with Coal as well - 2 factor solution and explore the 4 factor solution. Talk to Terre about the Slovic study and how they did it. 

```{r, echo = FALSE}

secopolall <- codedmodule2 %>%
        dplyr::select("WEALTHLIM","MECHANISATION","DECISIONDECEN","DECISIONCEN","INDUSTRYLARGE","INDUSTRYSMALL","ECONOMYGLOBAL","ECONOMYLOCAL", "ENVOVERDEV","DEVOVERENV","OWNERPVT","OWNERNOREG","OWNERPUB", "OWNERREG","DISPLACESOLAR",  "POLLUTESOLAR", "HEALTHSOLAR", "JOBSSOLAR", "BEAUTYSOLAR", "PRIDESOLAR", "NPRIDESOLAR", "DEVSOLAR", "PROSPERSOLAR", "RELYSOLAR", "SYSTEMDEMO")%>%
  na.omit()
secopolall_alpha <- psych::alpha(secopolall, check.keys = TRUE)

summary(secopolall_alpha) # 0.78



# PCA on all 
#secopolall_cor <- cor(secopolall)
#sPCA24 <- principal(secopolall, nfactors = 24, rotate = "none") # no rotation to start with. 

#print(sPCA24)

#sPCA24$loadings

#fa.parallel(secopolall_cor)

# this suggests 2 factors if we go by FA or 8 by PCA. let's try both and see how they look conceptually 

secopolall2.fa <- fa(secopolall, nfactors = 2, rotate = "varimax")

print.psych(secopolall2.fa, cut = 0.40,  sort = TRUE)

#fa.diagram(secopolall2.fa)

#cor(secopolall)



```


\newpage

# Coal - FA 2 factor solution

```{r, echo = FALSE}

cecopolall <- codedmodule2 %>%
        dplyr::select("WEALTHLIM","MECHANISATION","DECISIONDECEN","DECISIONCEN","INDUSTRYLARGE","INDUSTRYSMALL","ECONOMYGLOBAL","ECONOMYLOCAL", "ENVOVERDEV","DEVOVERENV","OWNERPVT","OWNERNOREG","OWNERPUB", "OWNERREG","DISPLACECOAL", "POLLUTECOAL", "HEALTHCOAL", "JOBSCOAL", "BEAUTYCOAL", "PRIDECOAL", "NPRIDECOAL", "DEVCOAL", "PROSPERCOAL", "RELYCOAL", "SYSTEMDEMO")%>%
  na.omit()
cecopolall_alpha <- psych::alpha(cecopolall, check.keys = TRUE)

summary(cecopolall_alpha) 


# PCA on all 
#secopolall_cor <- cor(secopolall)
#sPCA24 <- principal(secopolall, nfactors = 24, rotate = "none") # no rotation to start with. 

#print(sPCA24)

#sPCA24$loadings

#fa.parallel(secopolall_cor)

# this suggests 2 factors if we go by FA or 8 by PCA. let's try both and see how they look conceptually 

cecopolall2.fa <- fa(cecopolall, nfactors = 2, rotate = "varimax")

print.psych(cecopolall2.fa, cut = 0.40,  sort = TRUE)

#fa.diagram(cecopolall2.fa)

#cor(cecopolall)



```


\newpage
# Appendix1 

**Kahan et al (2007) scale**

Individualism - Communitarinism 

- **K_IINTRFER**	The government interferes far too much in our everyday lives.
- **K_IPRIVACY**	The government should stop telling people how to live their lives.
- **K_IPROTECT**	It’s not the government’s business to try to protect people from themselves.
- **K_SHARM**	    Sometimes the government needs to make laws that keep people from hurting themselves.
- **K_SLIMCHOI**	The government should put limits on the choices individuals can make so they don’t get in the way of what’s good for society.
- **K_SPROTECT**	The government should do more to advance society’s goals, even if that means limiting the freedom and choices of individuals.

Hierarchy -Egalitarianism

- **K_HEQUAL**	  We have gone too far in pushing equal rights in this country.
- **K_HREVDIS1**	Nowadays it seems like there is just as much discrimination against upper castes as there is against Dalits.
- **K_EDISCRIM**	Discrimination against minorities is still a very serious problem in our society.
- **K_ERADEQ1**	  We need to dramatically reduce inequalities between the rich and the poor.
- **K_EWEALTH**	  Our society would be better off if the distribution of wealth was more equal.
- **K_ERADEQ2**	  We need to dramatically reduce inequalities between men and women.

\newpage
# Appendix2 

 **New Eco-pol values scale**
 
- **DISPLACENUCLEAR**Nuclear energy is leading to displacement of people from their land
- **BEAUTYNUCLEAR**	 Nuclear energy spoils the natural beauty of the landscape
- **POLLUTENUCLEAR** Nuclear energy increases pollution of air/water/land
- **HEALTHNUCLEAR**	 Nuclear energy poses a great risk to the health of people living around it
- **JOBSNUCLEAR**	   Nuclear energy will bring jobs to the local community
- **PRIDENUCLEAR**	 I would be proud if my community used nuclear energy
- **NPRIDENUCLEAR**	 Nuclear energy is a mark of pride for our nation
- **DEVNUCLEAR**	   Nuclear energy pushes forward the country's development
- **PROSPERNUCLEAR** Nuclear energy brings economic prosperity to the surrounding regions
- **RELYNUCLEAR**	   I don't like the idea that I have to rely on the government for electricity from nuclear energy

- **DECISIONDECEN**	 Local politicians shouldn't have to ask permission from the central government to implement policies
- **DECISIONCEN**	   Laws and policies would be implemented more smoothly if more power lay with the central government.
- **INDUSTRYLARGE**	 Large scale industries are required for the development of the country that will benefit everyone
- **ECONOMYLOCAL**	 India would be better off if foreign companies didn't come to here
- **DEVOVERENV**	   Economic growth and creating jobs should be prioritized over environmental protection
- **INDUSTRYSMALL**	 Large corporations are destroying the local industries in India and benefiting only a handful of people.
- **WEALTHLIM**	     A limit should be put to how much wealth a person can amass
- **ECONOMYGLOBAL**	 Foreign companies have led to a range of benefits for the Indian people and society
- **OWNERPVT**	     All businesses and industries should be owned privately
- **OWNERPUB**	     The government should own most large businesses and industries
- **ENVOVERDEV**	   Polluting industries that spoil the environment should be shut down even if it costs people their jobs
- **OWNERREG**	     Regardless of ownership, the government should pass strong regulations and implement them
- **MECHANISATION**	 Rapid mechanization of work is taking away jobs from workers in this country
- **OWNERNOREG**	   There is too much red-tape and the government should not interfere with businesses and industries


